### 2025-09-04 download-football-data.qmd
20250904 - week 1 projected points

@@

We can download historical week-by-week actual player statistics using the `nflreadr::load_player_stats()` function from the `nflreadr` package [@R-nflreadr].
@HoPlayerStats provide a Data Dictionary for statistics for offensive players at the following link: <https://nflreadr.nflverse.com/articles/dictionary_player_stats.html>.
@HoPlayerStatsDefense provide a Data Dictionary for statistics for defensive players at the following link: <https://nflreadr.nflverse.com/articles/dictionary_player_stats_def.html>.
You can also access the data dictionary via `R` using the following syntax:

@@

players_projections_weekly_average <- players_projections_weekly_average %>% 
  add_ecr() %>% 
  #add_uncertainty() %>% # currently throws an error
  add_player_info()
```

@@

In addition to week-by-week actual player statistics, we can also compute historical actual player statistics as a function of different timeframes, including season-by-season and career statistics.

@@

Specify scoring settings:

>>>>

We can download historical actual player statistics as a function of different timeframes, including [week-by-week](#sec-downloadActualWeeklyStats) and [season-by-season](#sec-downloadActualSeasonalStats).

We can download historical week-by-week actual player statistics using the `nflreadr::load_player_stats()` function from the `nflreadr` package [@R-nflreadr].
Nevertheless, we could also calculate historical actual week-by-week statistics, as in @sec-calculateActualWeeklyStats
@HoPlayerStats provide a Data Dictionary for statistics for offensive players at the following link: <https://nflreadr.nflverse.com/articles/dictionary_player_stats.html>.
@HoPlayerStatsDefense provide a Data Dictionary for statistics for defensive players at the following link: <https://nflreadr.nflverse.com/articles/dictionary_player_stats_def.html>.
You can also access the data dictionary via `R` using the following syntax:

@@

@@

players_projections_weekly_average <- players_projections_weekly_average %>% 
  add_ecr() %>% 
  add_uncertainty() %>% # comment out if throws an error
  add_player_info()
```

@@

We can compute historical actual player statistics as a function of different timeframes, including [week-by-week](#sec-calculateActualWeeklyStats), [season-by-season](#sec-calculateActualSeasonalStats), and the [player's career](#sec-calculateActualCareerStats).

@@

We can then calculate players' historical actual fantasy points for [week-by-week](#sec-calculateActualPointsWeekly), [season-by-season](#sec-calculateActualPointsSeasonal), and the [player's career](#sec-calculateActualPointsCareer).
Specify scoring settings:
